\plaintitle

### 2016-09-16 drafts/labor/complexity.tex
intro notes resolved, some requests for feedback i also changed it so that \ali and \msb notes don't show up in the final document, but do show up in the constituent parts. if you want to undo that, comment lines 124-127 (or just 126-127)
incremental changes on complexity - still more to fix

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

% \renewcommand{\topic}[1]{#1}
\subsubsection[finding crowd work's limits]{Achieving greater complexity}\label{sec:complexity}
\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants%
, interpreting medical data, and
telling coherent and compelling stories%
, to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems%
, often involving insights made in Computer Science and applied to human work--flows.}

The crowd work literature typically identifies target milestones in computer science
that have presented significant challenges for researchers%
, leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge})%
, and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.
This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.
For example, \textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed%
, just like non--expert teams
\cite{foundry}.

\subsubsubsection{\pieceworkpers}
\msb{needs a transition to set the tone here. e.g., The piecework literature also examined the complexity limits possible with piecework.}
\topic{The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.}
\citeauthor{10.2307/23702539} describes a case study in Santa Fe Railway, which
deployed scientific management and a piecework regime in an attempt to stymie rising repair costs
\cite{10.2307/23702539}.
Returning to \citeauthor{hart2016rise}'s reflections on piecework's limitations,
we recall the multidimensional problem
--- tasks comprising of numerous, sometimes conflicting, goals
\cite{hart2016rise}.
It would be reasonable, then, to infer that work like this
--- reasonably highly skilled work where quality is difficult to assess ---
would be unsuitable for piecework. \msb{that conclusion came way too fast. give a little detail on the railway. how did they come to that conclusion?}

\msb{this paragraph needs a topic sentence. it's a wandering paragraph currently. is the claim here that evaluation is the limiting factor?}
\topic{\citeauthor{hart2016rise} and \citeauthor{10.2307/23702539}%
, without acknowledging one another%
, seemingly corroborate one another's conclusions at different levels of observation.}
\citeauthor{10.2307/23702539} enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and `experts'\dots''
\cite{hart2016rise,10.2307/23702539}.
\citeauthor{10.2307/23702539} and \citeauthor{hart2016rise} may seem
to be making differing claims about the limitations of piecework, but
we argue that \citeauthor{10.2307/23702539}
is simply making a more concrete observation illustrating the insight that
\citeauthor{hart2016rise} later makes. \msb{what insight? I've lost the thread here.}
\citeauthor{10.2307/23702539} recognizes that
it's necessary for a successful piecework shop to employ
clerks,
inspectors, and
other experts to properly design and evaluate complex work.
\citeauthor{hart2016rise} argues an ultimate limit to how far this can go;
at some point, evaluating multidimensional work output for quality
(rather than for quantity) becomes infeasible.

\topic{This isn't to say that complex work is outside of the realm of piecework;
indeed, we've discussed complex applications of crowd work already.}
As \citeauthor{hart2013rise} described,
the 1930s saw a flourishing of clever piecework job design out of necessity
due to the fact that it was infeasible to provide new workers with
the comprehensive education that was familiar to men
\cite{hart2013rise}.
This constraint led to much more tightly scoped work, and
(perhaps surprisingly at the time) more efficient allocations of workers,
who could now specialize in extremely narrowly defined roles.
The same could be said of Airy and his \textit{computers}
--- young boys whose preparations consisted principally of
a relatively specific mathematics curriculum
\cite{grier2013computers}. \msb{so what are we to take out of this? that there is no limit? just our creativity?}

\topic{Piecework researchers also make claims regarding
the organizations that benefit from piecework in the first place.} \msb{I think a reader wouldn't understand why that claim is relevant. Let's invert it, something like how the researchers point out that only certain kinds of organizations can effectively make use of piecework.}
\citeauthor{Brown01041990} discusses the factors necessary for piecework to thrive:
    ``\dots~incentive pay is less likely in jobs with
    a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990} \msb{that's confusing, is incentive pay the same as piecework? can you cut the first part of the quote and give us the noun instead of forcing us to figure it out?}.
\citeauthor{10.2307/23702539} adds further, that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.
Together, \citeauthor{10.2307/23702539} and \citeauthor{Brown01041990}
make a persuasive argument that piecework is limited in complexity by
managerial overhead \msb{wait, wasn't that in a previous paragraph? that should be joined with the managerial overhead text above} and the fixed cost of adopting a piecework payment regime \msb{that seems like it's the new point here}.

@@

\topic{Technology has made it possible
for non--experts to do work that was once considered
within the domain of experts.}
\msb{I don't yet buy the following argument. If the point is that technology makes us more expert, I disagree that the CrowdCrit/Voyant systems are using technology to do this. They are building the smarts into their OWN workflows, rather than giving workers EXTERNAL tools that make them smarter. Giving workers a calculator is an external tool; the mathematical tables project already demonstrated that you can build smarts into the workflow if you don't have one.}
\citeauthor{yuanAlmost} builds on the work of others
(\textit{Voyant} and, more relevantly, \textit{CrowdCrit})
to design workflows that yield ``expert--level feedback''
\cite{yuanAlmost,Xu:2014:VGS:2531602.2531604,Luther:2014:CCA:2556420.2556788}.
This body of work identifies ways to transform a variety of duties comprising complex tasks
and distills them into ``a narrow set of routinized duties''%
, informed in part by researchers --- acting as inspectors --- and experts
\cite[quotations from][]{10.2307/23702539}.
Where \citeauthor{10.2307/23702539} would call additionally for the identification of
crowdsourcing's version of ``piecework clerks'', we point out that
today algorithms manage workers as pieceworkers once did
\cite{uberAlgorithm,10.2307/23702539}.

\topic{Furthermore, technology more directly facilitates the subversion of expertise requirements
by giving non--experts access to information that would otherwise be unavailable.}
Taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity.
Researchers have identified significant growth of
the hippocampal regions of the brains in veteran drivers%
, generally understood to be responsible for spatial functions such as navigation
\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625%
,       skok2000managing,Woollett1407,woollett2011acquiring}.
Services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to know more about a city even than experts through
the collective data generated by other users
ranging topics such as police activity, congestion, construction, etc\dots
\cite{silva2013traffic,hind2014outsmarting}. \msb{what's the insight I should take away from this paragraph? what does this say about crowd work?}

@@

\onlyinsubfile{
  \printbibliography
  }

>>>>

\documentclass[trackingWork]{subfiles}
\onlyinsubfile{
  \usepackage{xr-hyper}
  \usepackage{hyperref}
}

\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

\subsubsection[What are the limits of crowd work]{Identifying the Limits of Crowd Work}\label{sec:complexity}
\subsubsubsection{\crowdworkpers}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems,
often involving insights made in Computer Science and applied to human work--flows.}
The crowd work literature typically identifies target milestones in computer science
that have presented significant challenges for researchers,
leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge}),
and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.
This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.
For example, \textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed,
just like non--expert teams
\cite{foundry}.

\subsubsubsection{\pieceworkpers}
\topic{Piecework researchers have found themselves trying to understand what characteristics limit piecework,
or more precisely what has prevented piecework from becoming more prevalent.}
The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.
\citeauthor{10.2307/23702539} describes a case study in Santa Fe Railway, which
deployed scientific management and a piecework regime in an attempt to stymie rising repair costs
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} reports on the hiring of Harrington Emerson,
an ``efficiency expert'', who went on to develop a ``standard time'' for each task at the company
informed by ``thousands of individual operations at the Topeka shops''.
The cost of measuring workers in such excruciating detail at the turn of the \nth{20} century was undoubtedly immense,
but this ``standard time'' value, which determined the pay that workers would earn for each task they do,
was the only viable approach at the time to determine appropriate pay given the task
\cite{10.2307/23702539}.
But the repeated measurement of workers' time to complete tasks had shortcomings;
for one thing, pay rates for rarer tasks
were necessarily less certain than for more common tasks,
which had the simple benefit of a larger sample size.
\ali{Do I need ``for another thing\dots''? This paragraph is kind of huge already. Not sure how to break it up/down as it is.}
One might conclude from \citeauthor{10.2307/23702539}'s observations that
complex, creative work --- which is inherently heterogeneous and difficult to routinize ---
would be unsuitable for piecework.
% We might reflect on \citeauthor{hart2016rise}'s piecework's limitations,
% and specifically the challenge of multidimensional work
% --- tasks comprising of numerous, sometimes conflicting, goals
% \cite{hart2016rise}.

% It would be reasonable, then, to infer that work like this
% --- reasonably highly skilled work where quality is difficult to assess ---
% would be unsuitable for piecework.
% \msb{that conclusion came way too fast. give a little detail on the railway. how did they come to that conclusion?}

% \msb{this paragraph needs a topic sentence. it's a wandering paragraph currently. is the claim here that evaluation is the limiting factor?}
\topic{Determining appropriate pay rates, informed by the careful measurement of workers,
isn't the only major challenge piecework faced; evaluation proved a limiting factor as well.}
\citeauthor{10.2307/23702539} enumerates some of the roles required
to facilitate piecework in the early \nth{20} century --- among them
    ``\dots~piecework clerks, inspectors, and `experts'\dots''
\cite{10.2307/23702539}.
% \citeauthor{10.2307/23702539} and \citeauthor{hart2016rise} may seem
% to be making differing claims about the limitations of piecework, but
% we argue that \citeauthor{10.2307/23702539}
% is simply making a more concrete observation illustrating the insight that
% \citeauthor{hart2016rise} later makes.
\citeauthor{10.2307/23702539} recognizes that
it's necessary for a successful piecework shop to employ
clerks,
inspectors, and
other experts to properly design and evaluate complex work.
\citeauthor{hart2016rise} later makes a more concrete observation of this hurdle,
as he argues an ultimate limit to how far this can go;
at some point, evaluating multidimensional work output for quality
(rather than for quantity) becomes infeasible.
In his words,
``if the quality of the output is more difficult to measure than the quantity,
perhaps because of `difficult--to--observe' production techniques,
then a piecework system is likely to encourage
an over--emphasis on quantity produced and an under-emphasis on quality''
\cite{hart2016rise}.
This, \citeauthor{hart2016rise} argues, may have fundamentally hamstrung piecework,
and ultimately precipitated its downfall,
especially with the increasing complexity of manufacturing work
over the course of the \nth{20} century.
\ali{just to be clear, this whole point is queuing up so that later I can be like
``Oh hey computers are terrific at evaluating some stuff really quickly.
And researchers in crowd work have done some work on workers evaluating other workers
(e.g. Find--Fix--Verify, arguably \textit{PeerStudio} does something along this line) \cite{bernsteinSoylent,Kulkarni:2015:PRP:2724660.2724670}''}

\topic{This isn't to say that complex work is outside of the realm of piecework;
indeed, we've discussed complex applications of crowd work already.}
As \citeauthor{hart2013rise} described,
the 1930s saw a flourishing of ingenious piecework design
almost strictly out of necessity ---
it was infeasible to provide new workers with
the comprehensive education that was familiar to men through apprenticeships
\cite{hart2013rise}.
This constraint led to much more tightly scoped work, and
(perhaps surprisingly at the time) more efficient allocations of workers,
who could now specialize in extremely narrowly defined roles.
The same could be said of Airy and his \textit{computers}
--- young boys whose preparations consisted principally of
a relatively specific mathematics curriculum
\cite{grier2013computers}.
Instead, the literature suggests that
piecework is tightly limited only when the application of piecework follows
a direct, perhaps even unimaginative,
mapping from an time--based regime to an output--based one.
When the work is redesigned from the ground up 
--- as we see with mathematicians in the \nth{19} century and
with the metalworking industry during the Second World War ---
it seems that we don't yet know the limits of complexity with regard to piecework.
% \msb{so what are we to take out of this? that there is no limit? just our creativity?}
\ali{This is \textit{almost} making a prediction,
but I wanted to take something punchy away from the stuff I cite here.}

\topic{Piecework researchers also argue that,
in addition to constraints on the kind of \textit{work} that's amenable to piecework,
only certain kinds of \textit{organizations} are amenable to piecework.}
% \msb{I think a reader wouldn't understand why that claim is relevant.
% Let's invert it, something like how
% the researchers point out that
% only certain kinds of organizations can effectively make use of piecework.}
\citeauthor{Brown01041990} discusses the organizational factors necessary for piecework to thrive,
arguing that piecework
``\dots~ is less likely in jobs with
a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}
% \msb{that's confusing, is incentive pay the same as piecework?
% can you cut the first part of the quote and
% give us the noun instead of forcing us to figure it out?}.
\citeauthor{10.2307/23702539} adds further, that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.
Together, \citeauthor{10.2307/23702539} and \citeauthor{Brown01041990}
make a persuasive argument that piecework is limited in complexity by
the capacity to endure managerial overhead while transitioning to a new system.
\msb{wait, wasn't that in a previous paragraph?
that should be joined with the managerial overhead text above}
\ali{I'm trying to make this argument that \cite{10.2307/23702539} is making two claims;
the first is that there are limits on doing hard, ``difficult--to--observe'' work,
and the second is that the cost propagates up to management,
putting limits on who can run piecework systems.
So\dots\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Rewrite\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Refactor\\
\makebox[0pt][l]{$\square$}\raisebox{.15ex}{\hspace{1em}} Drop}

@@

\topic{Technology has made it possible
for non--experts to do work that was once considered
within the domain of experts.}
\msb{I don't yet buy the following argument. If the point is that technology makes us more expert, I disagree that the CrowdCrit/Voyant systems are using technology to do this. They are building the smarts into their OWN workflows, rather than giving workers EXTERNAL tools that make them smarter. Giving workers a calculator is an external tool; the mathematical tables project already demonstrated that you can build smarts into the workflow if you don't have one.}
\citeauthor{yuanAlmost} builds on the work of others
(\textit{Voyant} and, more relevantly, \textit{CrowdCrit})
to design workflows that yield ``expert--level feedback''
\cite{yuanAlmost,Xu:2014:VGS:2531602.2531604,Luther:2014:CCA:2556420.2556788}.
This body of work identifies ways to transform a variety of duties comprising complex tasks
and distills them into ``a narrow set of routinized duties'',
informed in part by researchers --- acting as inspectors --- and experts
\cite[quotations from][]{10.2307/23702539}.
Where \citeauthor{10.2307/23702539} would call additionally for the identification of
crowdsourcing's version of ``piecework clerks'', we point out that
today algorithms manage workers as pieceworkers once did
\cite{uberAlgorithm,10.2307/23702539}.

\topic{Furthermore, technology more directly facilitates the subversion of expertise requirements
by giving non--experts access to information that would otherwise be unavailable.}
Taxi drivers in London endure rigorous training to pass a test known as ``The Knowledge''
--- a demonstration of the driver's comprehensive familiarity.
Researchers have identified significant growth of
the hippocampal regions of the brains in veteran drivers,
generally understood to be responsible for spatial functions such as navigation
\cite{Maguire11042000,Maguire2894,Skok:1999:KML:299513.299625,
      skok2000managing,Woollett1407,woollett2011acquiring}.
Services such as Google Maps \& Waze make it possible for
people entirely unfamiliar with a city
to know more about a city even than experts through
the collective data generated by other users
ranging topics such as police activity, congestion, construction, etc\dots
\cite{silva2013traffic,hind2014outsmarting}. \msb{what's the insight I should take away from this paragraph? what does this say about crowd work?}

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
}
